Modeling vertical-axis cross-flow turbine wakes

### 2015-03-21 paper.tex
Add mention of OpenFOAM
Add more details about numerical setup

@@

The RANS models employ a sliding mesh, where the turbine zone rotates at a mean
tip speed ratio $\lambda=1.9$ with an unsteadiness as the blade passage
frequency specified to mimic the experimental data.

@@

>>>>

In this study we set out to model the wake of the University of New Hampshire's
Reference Vertical-Axis (cross-flow) Turbine (UNH-RVAT) using a
Reynolds-averaged Navier--Stokes numerical model.

@@

\subsection{Computational mesh}

The RANS models employ a sliding mesh, where the turbine zone rotates at a mean
tip speed ratio $\lambda=1.9$ with an unsteadiness as the blade passage
frequency specified to mimic the experimental data. The 2-D mesh is shown in
Figure~\ref{fig:mesh}.

@@

3-D computer aided design (CAD) files of the turbine are available from
\cite{Bachant2014-RVAT-CAD}.

The 3-D mesh was also generated with \textit{OpenFOAM}'s \textit{snappyHexMesh}
application, with identical domain size, resolution, and boundary layer
parameters in the $x$--$y$ plane, and \todo[inline]{Get $N_z$ for 3-D mesh.}
cells in the vertical direction.

\begin{figure}[ht]
\caption{Snapshot of the 2-D computational mesh.}
\label{fig:mesh}
\end{figure}

\subsection{Software}

Simulations were run using the \textit{pimpleDyMFoam} solver from the
open-source finite volume CFD package \textit{OpenFOAM}, version 2.3.x.
